---
title: "NBA_FINAL"
author: "Guillem Bassa"
date: "18/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(rvest)
library(RSelenium)

```
View how many days we have downloades, to not repeat the process for all days
Note that the directory is from my machine, so you should change it to your directory (the one that you're saving the Rmarkdown file) for it to work.

```{r}
date_inic <- as.Date("2020-12-22") #first NBA game of the season
date_fin <- Sys.Date()
date_cont <- date_inic
days_no <- c()

while (date_fin != date_cont) {
  read_master <- as.character(paste0("C:/Users/Guillem/Documents/GitHub/Fantasy-NBA-2021//",as.character(date_cont),"_Master.csv"))
  
  if (!file.exists(read_master)) {
    days_no <- append(days_no, date_cont)
  }
  
  date_cont <- date_cont+1
 
}
#The 24 of December no match was played, so we remove it form the list
days_no <- days_no[-1]

```
Start the browser, note I've done that with Mozilla firefox

```{r}

browser <- rsDriver(browser = "firefox", port = 4545L, verbose = FALSE)
remDr <- browser[["client"]]

```



Modify the link to get data of specified day

```{r}
cont <- 1

for (day in days_no) {
  
  insert_day <- format((days_no[cont]), format = "%d")
  insert_month <-format((days_no[cont]), format = "%m")
  insert_year <- format((days_no[cont]), format = "%y")
  
  
  #Navigate
  pagina <- as.character(paste0("https://www.nba.com/stats/players/traditional/?sort=PTS&dir=-1&Season=2020-21&SeasonType=Regular%20Season&DateFrom=",insert_month,"%2F",insert_day,"%2F20", insert_year, "&DateTo=",insert_month,"%2F",insert_day,"%2F20", insert_year)) 
  remDr$navigate(pagina)
  
  Sys.sleep(25)

  if (cont == 1) {
    remDr$findElement(using = 'id', "onetrust-accept-btn-handler")$clickElement()
    Sys.sleep(15)
  }


remDr$findElement(using = 'xpath', "//*/option[@value = 'string:All']")$clickElement()

#get and modify the table

page_html <- remDr$getPageSource()[[1]]
table_html <- read_html(page_html) %>% #trobar la taula
  html_nodes("table") %>% 
  html_table(fill=T)


table_html_stats <- as.data.frame(table_html[[1]])

table_html_stats <- table_html_stats %>%
  rename(pos = 1) %>% 
  mutate(`3PTMissed` = `3PA` - `3PM`,
         `FG_Missed`= FGA - FGM,
         FTMissed = FTA - FTM)

table_html_stats <- table_html_stats %>% 
  select(-pos) %>% 
  mutate(score = PTS -FG_Missed - FTMissed + REB + AST +STL +BLK - TOV -PF + (W*2),
         day = as.factor(days_no[cont]))
save_name <- as.character(paste0("C:/Users/Guillem/Documents/GitHub/Fantasy-NBA-2021//",as.character(days_no[cont]),"_Data.csv"))

write.csv(table_html_stats,save_name, row.names = FALSE)


read_master <- as.character(paste0("C:/Users/Guillem/Documents/GitHub/Fantasy-NBA-2021//",as.character(as.Date(days_no[cont])-1),"_Master.csv"))

master <- read.csv(read_master)

colnames(table_html_stats) <- colnames(master) 

master <- rbind(master, table_html_stats)

master_save <- as.character(paste0("C:/Users/Guillem/Documents/GitHub/Fantasy-NBA-2021//",as.character(as.Date(days_no[cont])),"_Master.csv"))
master_save
  
write.csv(master,master_save, row.names = FALSE)
  
cont <- cont+1
 
}



```


## Graphics

Get to the ESPN page (previously you have to login)

```{r}
data <- read.csv(master_save)
data <- data %>% select(-(GP.RANK:X....RANK))
data7 <- data %>% 
  filter(day == as.character(Sys.Date()-8)|
           day == as.character(Sys.Date()-7)|
           day == as.character(Sys.Date()-6)|
           day == as.character(Sys.Date()-5)|
           day == as.character(Sys.Date()-4)|
           day == as.character(Sys.Date()-3)|
           day == as.character(Sys.Date()-2)|
           day == as.character(Sys.Date()-1)
           )



pagina_espn <-"https://fantasy.espn.com/basketball/players/add?leagueId=93039502"

remDr$navigate(pagina_espn)

Sys.sleep(20)

remDr$findElement(using = 'id', "onetrust-accept-btn-handler")$clickElement()

Sys.sleep(5)
```

Download the page with players I can get

```{r}
page_espn_html <- remDr$getPageSource()[[1]]
table_espn_html <- read_html(page_espn_html) %>% #trobar la taula
  html_nodes("table") %>% 
  html_table(fill=T)


table_espn <- as.data.frame(table_espn_html[[1]])
table_espn_2 <- as.data.frame(table_espn[1])

#Remove the teams

table_espn_2 <- table_espn_2 %>% 
  mutate(Players = gsub("GS.*","", Players),
         Players = gsub("Por.*","", Players),
         Players = gsub("Mil.*","", Players),
         Players = gsub("Min.*","", Players),
         Players = gsub("Sac.*","", Players),
         Players = gsub("LAL.*","", Players),
         Players = gsub("LAC.*","", Players),
         Players = gsub("Oln.*","", Players),
         Players = gsub("Dal.*","", Players),
         Players = gsub("Atl.*","", Players),
         Players = gsub("Cha.*","", Players),
         Players = gsub("Bkn.*","", Players),
         Players = gsub("ONY.*","", Players),
         Players = gsub("Den.*","", Players),
         Players = gsub("Orl.*","", Players),
         Players = gsub("Wsh.*","", Players),
         Players = gsub("Cle.*","", Players),
         Players = gsub("Mia.*","", Players),
         Players = gsub("OKC.*","", Players),
         Players = gsub("SA.*","", Players),
         Players = gsub("Bos.*","", Players),
         Players = gsub("Utah.*","", Players),
         Players = gsub("Phi.*","", Players),
         Players = gsub("Phx.*","", Players),
         Players = gsub("Ind.*","", Players),
         Players = gsub("Mem.*","", Players),
         Players = gsub("Det.*","", Players),
         Players = gsub("DTD.*","", Players)
         )

#Remove O  (Out)

table_espn_2 <- table_espn_2 %>% 
  mutate(Players = gsub("O$.*","", Players))


```

GET THE 10 PLAYERS THAT I CAN GET WITH MOST POINTS YESTERDAY

```{r}
name_list <- c(table_espn_2)

data7_can_get <- subset(data7, PLAYER %in% name_list[["Players"]])

data_today_can_get <- data7_can_get %>% 
  filter(day == as.character((Sys.Date()-1)))

data_today_top10_can_get <- data_today_can_get %>% 
  top_n(6,score)

mean_players <- data %>% 
  group_by(PLAYER) %>% 
  summarise(avg_season = mean(score))

data7_mean <- data7 %>% 
  group_by(PLAYER) %>% 
  summarise(avg_7 = mean(score))

data2 <- left_join(data, mean_players)
data2 <- left_join(data2, data7_mean)
```


```{r}
ggplot(subset(data2, PLAYER %in% data_today_top10_can_get$PLAYER), aes(as.Date(day),score, group = PLAYER, color = PLAYER))+
  geom_line()+
  stat_smooth(method = "lm")+
  ggtitle("Evolution of the 6 players avalaible with most points yesterday")+
  theme(legend.position = "none")+
  geom_hline(aes(yintercept = avg_season), linetype = "dashed")+
  geom_text(aes(label=score),hjust=0, vjust=0, size = 2.5, colour = "black")+
  geom_text(aes((Sys.Date()-2),avg_season, label = round(avg_season,1)), size = 3, vjust = 1)+
  geom_hline(aes(yintercept= avg_7), linetype = "dashed", color = "cyan")+
  facet_wrap(~PLAYER)


  
```


```{r}
data7_can_get_grouped <-data7_can_get %>% 
  group_by(PLAYER) %>% 
  summarise(avg_7 = mean(score))

top_data7 <-data7_can_get_grouped %>% 
  top_n(6,avg_7)


```

EVOLUTION OF THE 6 PLAYERS AVALIABLE WITH BETTER 7 DAY AVG

```{r}

ggplot(subset(data2, PLAYER %in% top_data7$PLAYER), aes(as.Date(day),score, group = PLAYER, color = PLAYER))+
  geom_line()+
  stat_smooth(method = "lm")+
  ggtitle("Evolution of the 6 players avalaible with better week average")+
  theme(legend.position = "none")+
  geom_hline(aes(yintercept = avg_season), linetype = "dashed")+
  geom_text(aes(label=score),hjust=0, vjust=0, size = 2.5, colour = "black")+
  geom_text(aes((Sys.Date()-2),avg_season, label = round(avg_season,1)), size = 3, vjust = 1)+
  geom_hline(aes(yintercept= avg_7), linetype = "dashed", color = "cyan")+
  facet_wrap(~PLAYER)



```




